%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Economics Analyst} % Job title
    {ENODA} % Organization
    {Edinburgh} % Location
    {Jul. 2024 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Promoted twice in two years (Intern $\to$ Assistant $\to$ Analyst); converted to full-time.}        \item {Deconstructed a legacy R workflow and rebuilt it, cutting run time by \textbf{98\%} (50s to $<$1s) by vectorising code and removing redundant I/O.}
        \item {Built a market-sizing model quantifying addressable revenue across \textbf{4 priority European markets}; presented to the CEO and fed the company's Series B investor narrative.}
        \item {Improved day-ahead price forecast accuracy by \textbf{25\% (RMSE)} over a benchmark, and deployed the models to run in real time on GCP.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Lead} % Job title
    {Castlecliffe Consultancy} % Organization
    {St Andrews} % Location
    {Jan. 2025 -- May 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Led a \textbf{5-analyst team} delivering EU/US macro and regulatory analysis to a US regional bank's Fixed Income desk; recommendations informed \textbf{\$50M+} in capital allocation decisions.}
        \item {Coordinated workstreams across analysts and synthesised outputs into client-ready briefings under a weekly delivery cadence.}
        \item {Built the models behind portfolio positioning; the client adopted \textbf{3 of 4} recommendations (\textbf{75\%} adoption rate).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Consultant} % Job title
    {Playfair Consultancy Group} % Organization
    {St Andrews} % Location
    {Sep. 2024 -- May 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Cut a sustainable-materials client's European market-entry timeline by \textbf{6 months}, narrowing \textbf{12 jurisdictions} to \textbf{3 priority markets} through comparative regulatory and demand analysis.}
        \item {Found a \textbf{15\%} supplier cost reduction via benchmarking, adopted in the client's partnership negotiations.}
        \item {Delivered a partnership strategy for an Alberta coffee roastery, including a \textbf{50+ partner directory} and outreach templates now in active client use.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Founder \& Head of Quantitative Research} % Job title
    {Elphinstone Capital Management} % Organization
    {St Andrews} % Location
    {Jun. 2025 -- Jun. 2026} % Date(s)
    {
      \begin{cvitems}
        \item {Founded a UK-wide student association from scratch, onboarding \textbf{20+ students} across \textbf{9 universities} and running it as a self-sustaining community.}
        \item {Standardised the onboarding process onto a shared platform, cutting time-to-productive from days to hours for every new member.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Head} % Job title
    {Mercury Capital Management} % Organization
    {St Andrews} % Location
    {Sep. 2024 -- Oct. 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Delivered \textbf{3 lectures} to \textbf{15 students}, translating technical model-validation and risk concepts for a mixed-experience audience.}
        \item {Guided a \textbf{4-person team} to a \textbf{top 5\%} finish in \textbf{IMC Prosperity 3} (\textbf{10,000+ participants}).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
