%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Economics Analyst} % Job title
    {ENODA} % Organization
    {Edinburgh} % Location
    {Jul. 2024 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Promoted twice in two years (Intern $\to$ Assistant $\to$ Analyst); converted to full-time.}
        \item {Built generalisable TAM model for ENODA's transformer product line, quantifying addressable revenue across \textbf{4 priority European markets}; presented to CEO and informing the company's Series B investor narrative.}
        \item {Cut day-ahead energy price forecast error by \textbf{25\% (RMSE)} versus an autoregressive benchmark in Polish wholesale electricity market.}
        \item {Reduced in-houe backtester computation time by \textbf{98\%} (50s to <1s) by vectorising legacy R codebase and eliminating redundant I/O.}
        \item {Deployed and maintained real-time execution of forecasting models on GCP.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Founder \& Head of Quantitative Research} % Job title
    {Elphinstone Capital Management} % Organization
    {St Andrews} % Location
    {Jun. 2025 -- Jun. 2026} % Date(s)
    {
      \begin{cvitems}
        \item {Founded a UK-wide ML and trading focused student association, onboarding \textbf{20+ students} from scratch and building a self-sustaining learning community.}
        \item {Architected containerised research platform adopted by \textbf{20 students} across \textbf{9 universities}; standardised workflows cut onboarding from days to hours.}
        \item {Led \textbf{3-person team} to \textbf{top 11 / 1,000+} in HKU x Avenir algorithmic trading competition with a cointegration-based strategy; ran live with \textbf{full P\&L responsibility on \$10K+ AUM} and \textbf{<5\% drawdown}.}
        \item {Won \textbf{Highest Trade Volume} award at Imperial Algothon 2026 (IMC-sponsored 24h hackathon) with a priority-queue scalping and market-making bot featuring inventory-skewed quotes (Avellaneda-Stoikov-inspired) and time-decaying edge thresholds.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Spring Insight Programmes} % Job title
    {Bloomberg Decoded; McKinsey Tech \& AI; Schroders Spring Insight} % Organization
    {London} % Location
    {Spring 2026} % Date(s)
    {
      \begin{cvitems}
        \item {1st place, Bloomberg Decoded EDA Challenge and Puzzle Challenge; 1st place, McKinsey Tech \& AI case competition.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Head} % Job title
    {Mercury Capital Management} % Organization
    {St Andrews} % Location
    {Sep. 2024 -- Oct. 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Ranked \textbf{1st across all cohorts} in internal algorithm competition; delivered highest risk-adjusted returns in fund history with a rank-based arbitrage CNN using a custom loss function.}
        \item {Led \textbf{4-person team} to \textbf{top 5\%} finish in \textbf{IMC Prosperity 3} (\textbf{10,000+ participants}) via market-making strategy with dynamic spread adjustment.}
        \item {Delivered \textbf{3 lectures} on model validation principles and risk management to \textbf{15 students}.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
