%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter

%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=1.2cm, right=1.4cm, bottom=1.2cm, footskip=.4cm}

% Color for highlights - Black and white theme
\definecolor{awesome}{HTML}{000000}
\definecolor{darktext}{HTML}{000000}
\definecolor{text}{HTML}{333333}
\definecolor{graytext}{HTML}{444444}
\definecolor{lighttext}{HTML}{666666}
\definecolor{sectiondivider}{HTML}{000000}

\setbool{acvSectionColorHighlight}{false}
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%-------------------------------------------------------------------------------
\name{Lev}{Rozanov}
\position{Quantitative Research{\enskip\cdotp\enskip}Algorithmic Trading{\enskip\cdotp\enskip}Mathematics \& Economics}
\address{St Andrews, Scotland, United Kingdom}

\mobile{(+44) 7444 058 016}
\email{l.rozanov@outlook.com}
\github{LevRoz630}
\linkedin{lev-rozanov}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%-------------------------------------------------------------------------------
\recipient
  {Da Vinci Recruitment}
  {Da Vinci\\Amsterdam, Netherlands}
\letterdate{\today}
\lettertitle{Application: Quant Trading Internship}
\letteropening{Dear Da Vinci Team,}
\letterclosing{Regards,}
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

\makecvheader[C]

\makecvfooter
  {}
  {Lev Rozanov~~~·~~~Cover Letter}
  {}

\makelettertitle

\begin{cvletter}

I built a live execution system on Binance: \$10K in capital, real-time order flow, inventory-based quoting. For IMC's competition I developed a market-making strategy with dynamic spread adjustment. I learned through iteration; Da Vinci's program structures that process.

Theory classes accelerate hypothesis formation: understanding spread dynamics before coding them into a strategy. Simulated trading compresses feedback on quoting and risk decisions; what I currently evaluate over weeks, I'd iterate on daily. Programming sessions build on ENODA work, where I cut computation latency by 98\% through vectorization. The project phase integrates all three.

I graduate in 2028 from Mathematics \& Economics at St Andrews. The intern-to-full-time pathway fits. I want to build a trading career here.

\end{cvletter}

\makeletterclosing

\end{document}
