%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter

%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=1.2cm, right=1.4cm, bottom=1.2cm, footskip=.4cm}

% Color for highlights - Black and white theme
\definecolor{awesome}{HTML}{000000}
\definecolor{darktext}{HTML}{000000}
\definecolor{text}{HTML}{333333}
\definecolor{graytext}{HTML}{444444}
\definecolor{lighttext}{HTML}{666666}
\definecolor{sectiondivider}{HTML}{000000}

\setbool{acvSectionColorHighlight}{false}
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%-------------------------------------------------------------------------------
\name{Lev}{Rozanov}
\position{Quantitative Research{\enskip\cdotp\enskip}Algorithmic Trading{\enskip\cdotp\enskip}Mathematics \& Economics}
\address{St Andrews, Scotland, United Kingdom}

\mobile{(+44) 7444 058 016}
\email{l.rozanov@outlook.com}
\github{LevRoz630}
\linkedin{lev-rozanov}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%-------------------------------------------------------------------------------
\recipient
  {IMC Trading Recruitment}
  {IMC Trading B.V.\\Amsterdam, Netherlands}
\letterdate{\today}
\lettertitle{Application: Launchpad Programme -- Trading}
\letteropening{Dear IMC Recruitment Team,}
\letterclosing{Regards,}
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

\makecvheader[C]

\makecvfooter
  {}
  {Lev Rozanov~~~·~~~Cover Letter}
  {}

\makelettertitle

\begin{cvletter}

I built a market-making strategy with dynamic spread adjustment that placed top 5\% among 10,000+ participants in IMC's global event. I now run a live execution system on Binance managing \$10K+ in capital. It processes order flow in real time and adjusts quotes based on inventory risk---the same core loop IMC operates at scale.

Speed under uncertainty is the edge. At ENODA I cut computation time by 98\% (50s to <1s) by eliminating bottlenecks in production code. Under timed pressure I placed top 11/1,000+ via statistical arbitrage and 1st across all cohorts in a separate event. Both required fast inference on incomplete data.

Trader mentorship will compress feedback loops on decisions I currently evaluate over weeks; simulation and poker pressure-test that inference live. I graduate in 2028, am UK-based, and available May 4--6.

\end{cvletter}

\makeletterclosing

\end{document}
