%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Machine Learning Researcher} % Job title
    {University of St Andrews -- School of Chemistry (Dr J.B.O. Mitchell)} % Organization
    {St Andrews} % Location
    {Apr. 2025 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Replicated state-of-the-art aqueous solubility prediction pipeline (Mitchell et al., \textit{ACS Omega} 2024) using LightGBM on \textbf{$\sim$14,000 compounds}; achieved \textbf{R\textsuperscript{2} = 0.92} and \textbf{RMSE = 0.57 log S}.}
        \item {Benchmarked tree-boosting methods (LightGBM, XGBoost) against graph neural networks, validating gradient boosting superiority on noisy molecular data with domain-specific feature engineering.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Quantitative Analyst} % Job title
    {ENODA} % Organization
    {Edinburgh} % Location
    {Jul. 2024 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Designed multi-horizon MLP forecasting pipeline for day-ahead electricity prices across European markets; architecture search yielded \textbf{12\% RMSE improvement} over autoregressive benchmark.}
        \item {Quantified marginal value of grid-operator features via regime-balanced evaluation; identified \textbf{6 statistically significant predictors} (p < 0.001) reducing forecast error by \textbf{7.1\%}.}
        \item {Reduced critical computation latency by \textbf{98\%} (\textbf{50s to <1s}) by vectorizing legacy R codebase and eliminating redundant I/O.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Head of Quantitative Research} % Job title
    {Elphinstone Capital Management} % Organization
    {St Andrews} % Location
    {Jun. 2025 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Deployed real-time execution system on Binance processing live order flow; managed \textbf{\$10K+ in live capital} with automated risk controls.}
        \item {Achieved \textbf{top 11 / 1,000+} in HKU x Avenir trading competition deploying cointegration-based statistical model on live orderbook data.}
        \item {Architected containerized research environment adopted by \textbf{15+ developers} across \textbf{5 universities}; reduced onboarding from days to hours.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Lead} % Job title
    {Mercury Capital Management} % Organization
    {St Andrews} % Location
    {Sep. 2024 -- Oct. 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Built CNN with custom loss function in TensorFlow/Keras optimizing risk-adjusted returns for fund-wide algorithm competition.}
        \item {Led \textbf{4-person team} in IMC Prosperity 3 (\textbf{10,000+ participants}), implementing market-making strategy with dynamic spread adjustment.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
