%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Economics Analyst} % Job title
    {ENODA} % Organization
    {Edinburgh} % Location
    {Jul. 2024 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Promoted twice in two years (Intern $\to$ Assistant $\to$ Analyst); converted to full-time.}
        \item {Eliminated \textbf{10+ hours/week} of manual analyst work by automating ETL pipelines; team redirected freed time to client-facing analysis.}
        \item {Cut client report latency by \textbf{98\%} (50s to <1s), unblocking same-day trading and dispatch decisions for energy desk.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Head of Quantitative Research} % Job title
    {Elphinstone Capital Management} % Organization
    {St Andrews} % Location
    {Jun. 2025 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Architected containerised research platform now used by \textbf{15+ analysts across 5 universities}; standardised workflows cut team onboarding from days to hours.}
        \item {Owned a live trading product end-to-end with \textbf{full P\&L responsibility on \$10K+ AUM}; ran incident response and rolling deployment for a 24/7 production system on Binance.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Lead} % Job title
    {Castlecliffe Consultancy} % Organization
    {St Andrews} % Location
    {Jan. 2025 -- May 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Informed \textbf{\$50M+} capital allocation decisions for US regional bank's Fixed Income desk through EU/US macro research and regulatory analysis.}
        \item {Achieved \textbf{75\%} recommendation adoption rate; client implemented 3 of 4 portfolio positioning strategies based on our econometric models.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Consultant} % Job title
    {Playfair Consultancy Group} % Organization
    {St Andrews} % Location
    {Sep. 2024 -- May 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Accelerated European market entry by \textbf{6 months} for sustainable materials client by identifying \textbf{3 priority markets} from 12 jurisdictions analysed.}
        \item {Enabled \textbf{15\%} supplier cost reduction through cost benchmarking analysis adopted in client's partnership negotiations.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
