%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Economics Analyst} % Job title
    {ENODA} % Organization
    {Edinburgh} % Location
    {Jul. 2024 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Promoted twice in two years (Intern $\to$ Assistant $\to$ Analyst); converted to full-time.}
        \item {Shipped ML forecasting pipelines (Python/R) now used in daily dispatch decisions for energy clients; improved day-ahead price prediction accuracy by \textbf{12\%}.}
        \item {Shipped automated ETL pipelines processing \textbf{2+ years} of hourly market data; eliminated \textbf{10+ hours/week} of manual work and cut report latency by \textbf{98\%} (50s to <1s).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Head of Quantitative Research} % Job title
    {Elphinstone Capital Management} % Organization
    {St Andrews} % Location
    {Jun. 2025 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Architected containerised platform now used by \textbf{15+ developers across 5 universities}; standardised workflows cut onboarding from days to hours.}
        \item {Built real-time trading system in Python deployed on Binance handling \textbf{\$10K+} in live trades; ran on-call for the 24/7 production system.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Head} % Job title
    {Mercury Capital Management} % Organization
    {St Andrews} % Location
    {Sep. 2024 -- Oct. 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Built CNN in TensorFlow/Keras with custom loss function; placed \textbf{1st across all years} in fund-wide algorithm competition.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
