%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Head of Quantitative Research} % Job title
    {Elphinstone Capital Management} % Organization
    {St Andrews} % Location
    {Jun. 2025 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Built real-time trading system in Python processing live market data, deployed on Binance handling \$10,000 in live trades.}
        \item {Architected Docker-based development environment adopted by 15+ student developers across 3 universities.}
        \item {Placed top 11 out of 1,000+ participants in HKU x Avenir WEB3 algorithmic trading competition.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Economic Assistant} % Job title
    {ENODA} % Organization
    {Edinburgh} % Location
    {Jul. 2024 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Developed ML forecasting pipelines in Python/R for energy markets, improving day-ahead prediction accuracy by 12\%.}
        \item {Refactored legacy codebase, reducing execution time of critical functions by 98\% (from 50s to <1s).}
        \item {Automated ETL pipelines processing 2+ years of hourly market data, eliminating 10+ hours/week of manual work.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Head} % Job title
    {Mercury Capital Management} % Organization
    {St Andrews} % Location
    {Sep. 2024 -- Oct. 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Built CNN in TensorFlow/Keras with custom loss function, ranked 1st across all years in fund-wide algorithm competition.}
        \item {Led 4-person team to top 5\% finish in IMC Trading Competition out of 10,000+ global participants.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Machine Learning Researcher} % Job title
    {University of St Andrews -- School of Chemistry} % Organization
    {St Andrews} % Location
    {Apr. 2025 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Developed ML models achieving 89\% accuracy in predicting molecular solubility across 5,000+ compound dataset.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
