%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Economics Analyst} % Job title
    {ENODA} % Organization
    {Edinburgh} % Location
    {Jul. 2024 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Promoted twice in two years (Intern $\to$ Assistant $\to$ Analyst); converted to full-time.}
        \item {Cut day-ahead energy price forecast error by \textbf{25\% (RMSE)} against an autoregressive benchmark in the Polish wholesale electricity market, applying statistical techniques to noisy live market data.}
        \item {Validated and hardened a legacy R backtester: vectorised the codebase and removed redundant I/O to cut run time \textbf{98\%} (50s to $<$1s), enabling faster model iteration and critique.}        \item {Deployed forecasting models to run in real time on GCP; promoted twice in two years and converted to full-time.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Founder \& Head of Quantitative Research} % Job title
    {Elphinstone Capital Management} % Organization
    {St Andrews} % Location
    {Jun. 2025 -- Jun. 2026} % Date(s)
    {
      \begin{cvitems}
        \item {Founded a UK-wide ML and trading student association, onboarding \textbf{20+ students} across \textbf{9 universities} onto a containerised research platform with standardised, reproducible workflows.}
        \item {Led \textbf{3-person team} to \textbf{top 11 / 1,000+} in the HKU x Avenir algorithmic trading competition with a cointegration-based strategy; ran live with \textbf{full P\&L responsibility on \$10K+ AUM}, holding drawdown \textbf{under 5\%} through disciplined risk sizing.}
        \item {Won \textbf{Highest Trade Volume} at Imperial Algothon 2026 (IMC-sponsored) with an inventory-skewed market-making bot (Avellaneda-Stoikov-inspired) using time-decaying edge thresholds.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Head} % Job title
    {Mercury Capital Management} % Organization
    {St Andrews} % Location
    {Sep. 2024 -- Oct. 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Delivered \textbf{3 lectures} on model validation principles and risk management to \textbf{15 students}, framing how to critique and stress models before trusting their output.}
        \item {Ranked \textbf{1st across all cohorts} in the internal algorithm competition; produced the highest risk-adjusted returns in fund history with a rank-based arbitrage CNN and a custom loss function.}
        \item {Guided a \textbf{4-person team} to a \textbf{top 5\%} finish in \textbf{IMC Prosperity 3} (\textbf{10,000+ participants}) with a market-making strategy using dynamic spread adjustment.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Lead} % Job title
    {Castlecliffe Consultancy} % Organization
    {St Andrews} % Location
    {Jan. 2025 -- May 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Led \textbf{5-analyst team} delivering EU/US macro and regulatory analysis to a US regional bank's Fixed Income desk; recommendations informed \textbf{\$50M+} in capital allocation.}
        \item {Built econometric models behind portfolio positioning; client adopted \textbf{3 of 4} recommendations and synthesised outputs into client-ready briefings on a weekly cadence.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Consultant} % Job title
    {Playfair Consultancy Group} % Organization
    {St Andrews} % Location
    {Sep. 2024 -- May 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Narrowed \textbf{12 jurisdictions} to \textbf{3 priority markets} for a materials client via comparative regulatory and demand analysis, accelerating market entry by \textbf{6 months}.}
        \item {Found a \textbf{15\%} supplier cost reduction through benchmarking, adopted in the client's partnership negotiations.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
