%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Head of Quantitative Research} % Job title
    {Elphinstone Capital Management} % Organization
    {St Andrews} % Location
    {Jun. 2025 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Deployed real-time execution system on Binance processing live order flow; managed \textbf{\$10K+ in live capital} with automated risk controls.}
        \item {Achieved \textbf{top 11 / 1,000+} in HKU x Avenir algorithmic trading competition using bucket cointegration strategy.}
        \item {Architected containerized research environment adopted by \textbf{15+ developers} across 3 universities; reduced onboarding time from days to hours.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Quantitative Analyst} % Job title
    {ENODA} % Organization
    {Edinburgh} % Location
    {Jul. 2024 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Improved day-ahead energy price forecasts by \textbf{12\%} by developing ensemble ML pipeline combining gradient boosting with feature engineering on weather/demand data.}
        \item {Reduced critical computation latency by \textbf{98\%} (50s → <1s) by vectorizing legacy R codebase and eliminating redundant I/O.}
        \item {Automated ETL pipelines processing \textbf{2+ years} of hourly market data; eliminated 10+ hours/week of manual data cleaning.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Lead} % Job title
    {Mercury Capital Management} % Organization
    {St Andrews} % Location
    {Sep. 2024 -- Oct. 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Ranked \textbf{1st across all years} in fund-wide algorithm competition by building CNN with custom loss function optimizing risk-adjusted returns.}
        \item {Led 4-person team to \textbf{top 5\%} finish in IMC Global Trading Competition (10,000+ participants) via market-making strategy with dynamic spread adjustment.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Machine Learning Researcher} % Job title
    {University of St Andrews -- School of Chemistry} % Organization
    {St Andrews} % Location
    {Apr. 2025 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Achieved \textbf{89\% accuracy} predicting molecular solubility across 5,000+ compounds using gradient boosting with domain-specific feature engineering.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
