%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Certifications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Quantitative Research Job Simulation} % Certification
    {J.P. Morgan via Forage} % Issuer
    {} % Location
    {Jun. 2026} % Date
    {
      \begin{cvitems}
        \item {Virtual experience covering natural gas commodity pricing, credit risk modelling in Python, and FICO score bucketing for a quant trading desk. Credential ID: LsyyNwoHaMNt4dkPz.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intro to Deep Learning} % Certification
    {Kaggle} % Issuer
    {} % Location
    {Jun. 2025} % Date
    {
      \begin{cvitems}
        \item {Built and trained neural networks in TensorFlow/Keras: activation functions, SGD/Adam optimisers, regularisation (dropout, batch normalisation), and binary classification.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intermediate Machine Learning} % Certification
    {Kaggle} % Issuer
    {} % Location
    {Jun. 2025} % Date
    {
      \begin{cvitems}
        \item {Handled missing values, categorical encoding, sklearn pipelines, cross-validation, gradient boosting (XGBoost), and data leakage diagnosis.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Learn R} % Certification
    {Codecademy} % Issuer
    {} % Location
    {May 2025} % Date
    {
      \begin{cvitems}
        \item {R fundamentals, data manipulation with dplyr and tidyr, descriptive statistics and hypothesis testing, and visualisation with ggplot2.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Investment Risk Management} % Certification
    {Coursera} % Issuer
    {} % Location
    {Feb. 2024} % Date
    {
      \begin{cvitems}
        \item {Portfolio risk analysis using the Treynor ratio and Value at Risk (VaR); risk-to-reward quantification and loss estimation under normal market conditions.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
