%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Economics Analyst} % Job title
    {ENODA} % Organization
    {Edinburgh} % Location
    {Jul. 2024 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Cut day-ahead electricity price forecast error by \textbf{25\% (RMSE)} versus an autoregressive benchmark using an ML model on Polish wholesale market data.}
        \item {Vectorised a legacy R backtester and removed redundant I/O, cutting computation time by \textbf{98\%} (50s to $<$1s).}
        \item {Promoted twice in two years (intern to analyst) and converted to full-time; built a generalisable modelling framework adopted across \textbf{4 European markets}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Spring Insight Programmes} % Job title
    {Bloomberg Decoded; McKinsey Tech \& AI; Schroders Spring Insight} % Organization
    {London} % Location
    {Spring 2026} % Date(s)
    {
      \begin{cvitems}
        \item {Won 1st place in the Bloomberg Decoded EDA and Puzzle Challenges and the McKinsey Tech \& AI case competition, across three selective spring programmes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Founder \& Head of Quantitative Research} % Job title
    {Elphinstone Capital Management} % Organization
    {St Andrews} % Location
    {Jun. 2025 -- Jun. 2026} % Date(s)
    {
      \begin{cvitems}
        \item {Founded a UK-wide ML and quantitative trading student association; onboarded \textbf{20+ students} across \textbf{9 universities} onto a containerised research platform that cut setup from days to hours.}
        \item {Led a \textbf{3-person team} to \textbf{top 11 / 1,000+} in the HKU x Avenir algorithmic trading competition with a cointegration-based strategy; ran it live with \textbf{full P\&L on \$10K+ AUM} at \textbf{$<$5\% drawdown}.}
        \item {Won \textbf{Highest Trade Volume} at Imperial Algothon 2026 (IMC-sponsored) with a market-making bot using inventory-skewed quotes (Avellaneda-Stoikov-inspired) and time-decaying edge thresholds.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Head} % Job title
    {Mercury Capital Management} % Organization
    {St Andrews} % Location
    {Sep. 2024 -- Oct. 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Ranked \textbf{1st across all cohorts} in the internal algorithm competition, delivering the highest risk-adjusted returns in fund history with a rank-based arbitrage CNN and a custom loss function.}
        \item {Guided a \textbf{4-person team} to a \textbf{top 5\%} finish in \textbf{IMC Prosperity 3} (\textbf{10,000+ participants}) with a market-making strategy using dynamic spread adjustment.}
        \item {Taught \textbf{3 lectures} on model validation and risk management to \textbf{15 students}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Lead} % Job title
    {Castlecliffe Consultancy} % Organization
    {St Andrews} % Location
    {Jan. 2025 -- May 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Built econometric models behind fixed-income portfolio positioning for a US regional bank's desk; the client adopted \textbf{3 of 4} recommendations, informing \textbf{\$50M+} in capital allocation.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
